Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-07 paper.qmd
Updated Figure 10 labels

trimesh_two_curvy2 <- ggplot() +
  geom_segment(data = tr_from_to_df_two_curvy2,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = umap_two_curvy_scaled,
             aes(
               x = UMAP1,
               y = UMAP2
             ),
             color = "#636363",
            alpha = 0.5,
            size = 0.5
            ) +
  coord_equal() +
  interior_annotation("a1")

@@

trimesh_two_curvy_removed1 <- ggplot() +
  geom_segment(data = tr_from_to_df_two_curvy3,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000")+
  geom_point(data = umap_two_curvy_scaled,
             aes(
               x = UMAP1,
               y = UMAP2
             ),
             color = "#636363",
            alpha = 0.5,
            size = 0.5
            ) +
  coord_equal() +
  interior_annotation("c1")

@@

trimesh_two_curvy_removed2 <- ggplot() +
  geom_segment(data = tr_from_to_df_two_curvy4,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000")+
  geom_point(data = umap_two_curvy_scaled,
             aes(
               x = UMAP1,
               y = UMAP2
             ),
             color = "#636363",
            alpha = 0.5,
            size = 0.5
            ) +
  coord_equal() +
  interior_annotation("b1")

@@

two_curvy_proj_umap_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") + #31a354
  geom_point(
    size = 0.5,
    alpha = 0.5,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.126, 0.125)) + 
  ylim(c(-0.126, 0.125)) +
  interior_annotation("c2") +
  theme(
    legend.position = "none"
  )

two_curvy_proj_umap_model_delaunay <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df1, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") + #31a354
  geom_point(
    size = 0.5,
    alpha = 0.5,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.126, 0.125)) + 
  ylim(c(-0.126, 0.125)) +
  interior_annotation("a2") +
  theme(
    legend.position = "none"
  )

two_curvy_proj_umap_model_benchmark2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df2, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") + #31a354
  geom_point(
    size = 0.5,
    alpha = 0.5,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.126, 0.125)) + 
  ylim(c(-0.126, 0.125)) +
  interior_annotation("b2") +
  theme(
    legend.position = "none"
  )

>>>>

trimesh_two_curvy2 <- ggplot() +
  geom_segment(data = tr_from_to_df_two_curvy2,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = umap_two_curvy_scaled,
             aes(
               x = UMAP1,
               y = UMAP2
             ),
             color = "#636363",
            alpha = 0.5,
            size = 0.5
            ) +
  coord_equal() +
  interior_annotation("a1", sc_ltr_pos)

@@

trimesh_two_curvy_removed1 <- ggplot() +
  geom_segment(data = tr_from_to_df_two_curvy3,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000")+
  geom_point(data = umap_two_curvy_scaled,
             aes(
               x = UMAP1,
               y = UMAP2
             ),
             color = "#636363",
            alpha = 0.5,
            size = 0.5
            ) +
  coord_equal() +
  interior_annotation("c1", sc_ltr_pos)

@@

trimesh_two_curvy_removed2 <- ggplot() +
  geom_segment(data = tr_from_to_df_two_curvy4,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000")+
  geom_point(data = umap_two_curvy_scaled,
             aes(
               x = UMAP1,
               y = UMAP2
             ),
             color = "#636363",
            alpha = 0.5,
            size = 0.5
            ) +
  coord_equal() +
  interior_annotation("b1", sc_ltr_pos)

@@

two_curvy_proj_umap_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") + #31a354
  geom_point(
    size = 0.5,
    alpha = 0.5,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.126, 0.125)) + 
  ylim(c(-0.126, 0.125)) +
  interior_annotation("c2", sc_ltr_pos) +
  theme(
    legend.position = "none"
  )

two_curvy_proj_umap_model_delaunay <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df1, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") + #31a354
  geom_point(
    size = 0.5,
    alpha = 0.5,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.126, 0.125)) + 
  ylim(c(-0.126, 0.125)) +
  interior_annotation("a2", sc_ltr_pos) +
  theme(
    legend.position = "none"
  )

two_curvy_proj_umap_model_benchmark2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df2, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") + #31a354
  geom_point(
    size = 0.5,
    alpha = 0.5,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.126, 0.125)) + 
  ylim(c(-0.126, 0.125)) +
  interior_annotation("b2", sc_ltr_pos) +
  theme(
    legend.position = "none"
  )
